\sysfull

### 2018-04-17 paper/implementation.tex
impl: missing preposition
impl: interruptible by async events

\textbf{Protected Variables.} The \texttt{COALA\_PV} annotation on a
variable statically allocates and aligns a protected non-volatile variable. The
variable must then be accessed \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.

\textbf{Task Transitions.} A call to \texttt{COALA\_NEXT\_TASK} immediately
transfers control to a specified next task and this API can be invoked along
any arbitrary control path (i.e., to dynamically determine the next task).
Like prior work~\cite{chain,dino,ratchet}, \sys's task control-flow model
assumes that an executing task is never interrupted.

>>>>

\textbf{Task Transitions.} A call to \texttt{COALA\_NEXT\_TASK} immediately
transfers control to a specified next task and can be invoked along
any control path to dynamically determine the next task.
Like prior work~\cite{chain,dino,ratchet}, \sys's control-flow model
assumes that an executing task is not interruptible by asynchronous events.

\textbf{Protected Variables.} The \texttt{COALA\_PV} annotation on a
variable statically allocates and aligns a protected non-volatile variable. The
variable must then be accessed with the \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.
